A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-12 BSS7782.tex
testing

Even more curious, there exists in the old open cluster NGC 188 a
double BS binary, called Binary 7782.  More generally, the BS population in NGC 188 has a bi-modal period-eccentricity distribution.  As discussed in \citet{leigh11}, this could be hinting at a triple origin for at least some subset of the total BS population.  As for Binary 7782, \citet{mathieu09}
observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
star system with an orbital period of $\sim$ 10 days hosting two blue
stragglers.  During a given binary-binary interaction, the probability
that not one but two direct (ms, ms) collisions occur is less than
$10^{-2}$ \citep{leonard89,leigh11,leigh12}.  Typically, such binaries
have long orbital periods. Dynamically, it is difficult to form a
short-period binary composed of two collision products during a
collision interaction in a star cluster \citep{2011Sci...334.1380F}.
So, how did Binary 7782 form?

@@

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_minimumstablesize.pdf}
\caption{Orbital separation as a function of the mass of the
  Roche-lobe filling outer star. The red curves gives the size at the
  first giant branch (thick curve) at the AGB (thin curve). The
  blue curve gives the orbital separation at the moment this giant fills its
  Roche-lobe assuming a circular orbit and a total inner binary mass
  of 2.0\,\MSun. The green curves give, under these conditions, the
  maximum orbital separation for a stable inner binary.
\label{fig:tertiarymass_vs_size}}
\end{figure}

>>>>

Even more curious, there exists in the old open cluster NGC 188 a
double BS binary, called Binary 7782.  More generally, the BS population in NGC 188 has a bi-modal period-eccentricity distribution.  As discussed in \citet{leigh11}, this could be hinting at a triple origin for at least some subset of the total BS population.  As for Binary 7782, \citet{mathieu09}
observed a compact and mildly eccentric (i.e., e $\sim$ 0.1) binary
star system with an orbital period of $\sim$ 10 days hosting two roughly equal-mass blue
stragglers.  During a given binary-binary interaction, the probability
that not one but two direct (ms, ms) collisions occur is less than
$10^{-2}$ \citep{leonard89,leigh11,leigh12}.  Typically, such binaries
have long orbital periods. Dynamically, it is difficult to form a
short-period binary composed of two collision products during a
collision interaction in a star cluster \citep{2011Sci...334.1380F}.
So, how did Binary 7782 form?

@@

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_minimumstablesize.pdf}
\caption{Orbital separation as a function of the mass of the
  Roche-lobe filling outer star. The red curves gives the size r$_{\rm 3}$ at the
  first giant branch (thick curve) and at the AGB (thin curve). The
  blue curve gives the orbital separation a$_{\rm RLOF}$ at the moment this giant fills its
  Roche-lobe assuming a circular orbit and a total inner binary mass
  of 2.0\,\MSun. The green curves give, under these conditions, the
  maximum orbital separation for a stable inner binary or a$_{\rm stable}$.
\label{fig:tertiarymass_vs_size}}
\end{figure}
